\documentclass[12pt]{article}

\usepackage{amsfonts,amssymb,amsmath}
\usepackage{setspace,achicago,graphicx,url}

%for avoiding figures going anywhere
\usepackage{placeins}

%\usepackage{hyperref}

\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newenvironment{proof}[1][Proof]{\noindent \textbf{#1.} }{\  \rule{0.5em}{0.5em}}


\usepackage{xr-hyper} % to allow links to the appendix
\externaldocument[O-]{prohibitorum-appendix}
\externaldocument[M-]{prohibitorum}

\usepackage[compact]{titlesec}  %to compact titles

%for building table 2
\usepackage{tabularx,booktabs,arydshln}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}


\usepackage[top=.9in, bottom=.9in, left=.9in , right=.9in,letterpaper]{geometry}

%for nice caption in table
\usepackage{caption}
\captionsetup[table]{skip=5pt}

%For accepting graphs
\usepackage{graphicx}

%Timeline of events
\usepackage{chronosys}

%For subtables
\usepackage{subcaption}
\usepackage[justification=centering]{caption}


%for building table 2
\usepackage{tabularx,booktabs,arydshln}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Other Packages%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%Within Document References
%\usepackage[colorlinks]{hyperref}
%\usepackage[colorinlistoftodos]{todonotes}
%\usepackage[colorlinks]{hyperref}
%\usepackage[nameinlink,capitalize,noabbrev]{cleveref}

%\hypersetup{
%	colorlinks,
%	linkcolor={blue!50!black},
%	citecolor={blue!50!black},
%	urlcolor={blue!80!black}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parskip3mm\parindent0cm


\title{Catholic Censorship and the Demise of Knowledge Production in Early Modern Italy}
\author{Fabio Blasutto$^1$ \and David de la Croix$^2$}



\begin{document}
\maketitle


\begin{abstract}
Censorship makes new ideas less available to others, but also reduces the share of people choosing to develop non-compliant ideas.
We propose a new method to measure the effect of censorship on knowledge growth,  accounting for the agents' choice between compliant and non-compliant occupations. We apply our method to the Catholic Church's censorship of books written by members of Italian universities and academies over the period 1400-1750. We highlight two new facts: once censorship was introduced, censored authors were of better quality than the non-censored authors, but this gap shrank over time, and the intensity of censorship decreased over time. These facts are used to identify the deep parameters of a novel endogenous growth model linking censorship to knowledge diffusion and occupational choice. We conclude that censorship reduced by 34\% the average log publication per scholar in Italy, while adverse macroeoconomic processes are responsible for another 9\% reduction. Interestingly, the induced reallocation of talents towards compliant activities explains half the effect of censorship.

\mbox{ }\\
JEL Classification Numbers: J24, N33, O33, O43. \\
Keywords: Censorship, Upper-Tail Human Capital, Publications, Scholars, Early Modern Italy, Occupational Choice
\end{abstract}

\footnotetext[1]{Department of Economics, Stockholm School of Economics. Email: fabio.blasutto@hhs.se}
\footnotetext[2]{IRES/LIDAM, UCLouvain \& CEPR. Email: david.delacroix@uclouvain.be.\\
\indent This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme, under grant agreement No 883033 ``Did elite human capital trigger the rise of the West? Insights from a new database of European scholars.'' Blasutto acknowledges financial support from the French speaking community of Belgium (\textit{mandat d'aspirant} FC 23613). We thank Matthias Doepke, Fabio Mariani, Joel Mokyr, and Luca Pensieroso for their thoughts on an earlier version of the paper.}

\thispagestyle{empty}
\newpage
\onehalfspacing

\input{introduction.tex}
\input{data.tex}
\input{model.tex}
\input{estimation.tex}
\input{conclusion.tex}

\clearpage

\onehalfspacing



\renewcommand\thefigure{\thesection.\arabic{figure}}
\renewcommand\thetable{\thesection.\arabic{table}}


\appendix
\input{appendix-data.tex}
\input{appendix-biblio.tex}
\input{appendix-proofs.tex}

\clearpage

\bibliographystyle{achicago}
\bibliography{prohibitorum}




\end{document}
