\documentclass[12pt]{article}

\usepackage{amsfonts,amssymb,amsmath,enumitem,booktabs}
\usepackage{setspace,achicago,graphicx,url}

%for avoiding figures going anywhere
%\usepackage{placeins}

%\usepackage{hyperref}

\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newenvironment{proof}[1][Proof]{\noindent \textbf{#1.} }{\  \rule{0.5em}{0.5em}}


\usepackage{xr-hyper} % to allow links to the appendix
\externaldocument[O-]{prohibitorum-appendix}

\usepackage[compact]{titlesec}  %to compact titles



\usepackage[top=.9in, bottom=.9in, left=.9in , right=.9in,letterpaper]{geometry}

%for nice caption in table
\usepackage{caption}
\captionsetup[table]{skip=5pt}

%For accepting graphs
\usepackage{graphicx}

%Timeline of events
\usepackage{chronosys}

%For subtables
\usepackage{subcaption}
\usepackage[justification=centering]{caption}


%for building table 2
\usepackage{tabularx,booktabs,arydshln}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}


\parskip3mm\parindent0cm


\title{Catholic Censorship and the Demise of Knowledge Production in Early Modern Italy}
\author{Fabio Blasutto$^1$ \and David de la Croix$^2$}



\begin{document}
\maketitle


\begin{abstract}
Censorship makes new ideas less available to others, but also reduces the share of people choosing to develop non-compliant ideas.
We propose a new method to measure the effect of censorship on knowledge growth,  accounting for the agents' choice between compliant and non-compliant occupations. We apply our method to the Catholic Church's censorship of books written by members of Italian universities and academies over the period 1400-1750. We highlight  new facts: once censorship was introduced, censored authors were of better quality than the non-censored authors, but this gap shrank over time, and the intensity of censorship decreased over time. These facts are used to identify the deep parameters of a novel endogenous growth model linking censorship to knowledge diffusion and occupational choice. We conclude that censorship reduced by 35\% the average log publication per scholar in Italy, while adverse macroeconomic processes are responsible for another 9\% reduction. The induced reallocation of talents towards compliant activities explains half the effect of censorship.

\mbox{ }\\
JEL Classification Numbers: J24, N33, O33, O43. \\
Keywords: Censorship, Upper-Tail Human Capital, Publications, Scholars, Early Modern Italy, Occupational Choice
\end{abstract}

\footnotetext[1]{Department of Economics, Stockholm School of Economics. Email: fabio.blasutto@hhs.se}
\footnotetext[2]{IRES/LIDAM, UCLouvain \& CEPR. Email: david.delacroix@uclouvain.be.\\
\indent This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme, under grant agreement No 883033 ``Did elite human capital trigger the rise of the West? Insights from a new database of European scholars.'' Blasutto acknowledges financial support from the French speaking community of Belgium (\textit{mandat d'aspirant} FC 23613). We thank Fabrice Collard, Matthias Doepke, Fabio Mariani, Joel Mokyr, and Luca Pensieroso for their thoughts on an earlier version of the paper. We also benefitted from comments during seminars at Northwestern, Luiss, GATE Lyon,  U. Padova, and Toulouse School of Economics. We thank the research assistants who have helped us with data collection, in particular Mara Vitale, Gaia Spolverini, Cecilia Rolla, and Chiara Zanardello.}

\thispagestyle{empty}
\newpage
\onehalfspacing

\input{introduction.tex}
\input{data.tex}
\input{model.tex}
\input{estimation.tex}
\input{conclusion.tex}


\bibliographystyle{achicago}
\bibliography{prohibitorum}



\end{document}
